---
title: "Inscribe Student Activity Analysis"
author: "Pramath Shukla"
date: "2024-03-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(knitr)
library(ggplot2)
```

# Students Enrolled in Inscribe community compared to number of students enrolled in class section

Total students enrolled in Inscribe community for Spring 2024 are 232

Total students enrolled in respective class sections are 574

\vspace{10mm}

```{r compareEnrollment, echo=FALSE}
# Example data frame
my_data <- data.frame(
  Sections = c(" 13081", "16190", "18392", "26576", "26763", "37447"),
  Section_Enrollment = c(100, 97, 97, 102,103, 75),
  Inscribe_Enrollment = c(0,0,30,75,79,48)
)
# Transpose the data frame
my_data_transposed <- t(my_data)

# Create a table using kable
table <- kable(my_data_transposed, format = "markdown")

table 
```

\vspace{10mm}

```{r plotEnrollment, echo=FALSE}
my_data_new <- data.frame(
  Sections = c("18392", "26576", "26763", "37447"),
  Section_Enrollment = c(97, 102,103, 75),
  Inscribe_Enrollment = c(30,75,79,48)
)

# Reshape the data for ggplot2
my_data_long <- tidyr::gather(my_data_new, key = "Enrollment_Type", value = "Enrollment", -Sections)

# Create a grouped bar plot
plot <- ggplot(my_data_long, aes(x = Sections, y = Enrollment, fill = Enrollment_Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Enrollment Comparison by Section",
       x = "Sections",
       y = "Enrollment",
       fill = "Enrollment Type") +
  theme_minimal() + theme(
    text = element_text(size = 10)  # Adjust the font size here (change 10 to your desired size)
  )
plot
```

# Questions posted by students in Inscribe community 

Number of students who posted questions in Inscribe community are 59. (It also includes students who just posted in Math Study Hall Channel)

Total students enrolled in inscribe 232

Percentage of students : 17.77%

\vspace{10mm}

```{r Questions, echo=FALSE}
# Example data frame
my_data <- data.frame(
  Sections = c("18392", "26576", "26763", "37447"),
  Inscribe_Enrollment = c(30,75,79,48),
  Questions_Asked = c(2,19,11,14),
  Percentage = c(6.67,25.33,13.92,29.17)
)
# Transpose the data frame
my_data_transposed <- t(my_data)

# Create a table using kable
table <- kable(my_data_transposed, format = "markdown")

table 
```

\vspace{10mm}

```{r plotQuestions, echo=FALSE}
my_data <- data.frame(
  Sections = c("18392", "26576", "26763", "37447"),
  Inscribe_Enrollment = c(30,75,79,48),
  Questions_Asked = c(2,19,11,14),
  Percentage = c(6.67,25.33,13.92,29.17)
)

# Reshape the data for ggplot2
my_data_long <- tidyr::gather(my_data, key = "Variable", value = "Value", -Sections)

# Create a grouped bar plot
ggplot(my_data_long, aes(x = Sections, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison between Inscribe Enrollment and Questions Asked",
       x = "Sections",
       y = "Count",
       fill = "Variable") +
  theme_minimal()
```

\clearpage

# Students who just viewed questions and question threads

Number of students who viewed questions in Inscribe community are 151. (It also includes students who just viewed questions from Math Study Hall Channel)

Total students enrolled in inscribe 232

Percentage of students : 68.97%

\vspace{10mm}

```{r QuestionsViewed2024, echo=FALSE}
# Example data frame
my_data <- data.frame(
  Sections = c("18392", "26576", "26763", "37447"),
  Inscribe_Enrollment = c(30,75,79,48),
  Questions_Viewed = c(12,51,39,37),
  Percentage = c(40.00,68.00,49.37,77.08)
)
# Transpose the data frame
my_data_transposed <- t(my_data)

# Create a table using kable
table <- kable(my_data_transposed, format = "markdown")

table 
```

\vspace{10mm}

```{r plotQuestionsViewed2024, echo=FALSE}
my_data <- data.frame(
  Sections = c("18392", "26576", "26763", "37447"),
  Inscribe_Enrollment = c(30,75,79,48),
  Questions_Viewed = c(12,51,39,37),
  Percentage = c(40.00,68.00,49.37,77.08)
)

# Reshape the data for ggplot2
my_data_long <- tidyr::gather(my_data, key = "Variable", value = "Value", -Sections)

# Create a grouped bar plot
ggplot(my_data_long, aes(x = Sections, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison between Inscribe Enrollment and Questions Asked",
       x = "Sections",
       y = "Count",
       fill = "Variable") +
  theme_minimal()
```

\clearpage


# Students who viewed questions/threads and also gave reactions

Number of students who viewed questions and question threads : 151

Number of students who also gave reactions : 45

Percentage of students who gave reactions : 29.80%

\vspace{10mm}

```{r ReactionsGiven2024, echo=FALSE}
# Example data
data <- data.frame(
  Category = c("Viewed", "Gave Reactions", "Did Not Give Reactions"),
  Count = c(151, 45, 151 - 45),
  Percentage = c(100, 29.80, 100 - 29.80)
)

# Create a bar plot
ggplot(data, aes(x = Category, y = Count, fill = Category)) +
  geom_bar(stat = "identity", color = "white") +
  labs(title = "Students' Interaction with Questions",
       y = "Number of Students") +
  geom_text(aes(label = paste0(Count, " (", sprintf("%.2f", Percentage), "%)")),
            position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  theme(legend.position = "none")

```

\clearpage

# Students enrolled in inscribe community who posted a resource

Total number of students enrolled : 232

Number of students who posted resources : 49

Percentage of students who posted resources : 21.12%

\vspace{10mm}

```{r PostedResources2024, echo=FALSE}
# Example data
data <- data.frame(
  Category = c("Enrolled", "Posted Resources", "Did Not Posted Resource"),
  Count = c(232, 49, 232 - 49),
  Percentage = c(100, 21.12, 100 - 21.12)
)

# Create a bar plot
ggplot(data, aes(x = Category, y = Count, fill = Category)) +
  geom_bar(stat = "identity", color = "white") +
  labs(title = "Students' Interaction with Resources",
       y = "Number of Students") +
  geom_text(aes(label = paste0(Count, " (", sprintf("%.2f", Percentage), "%)")),
            position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  theme(legend.position = "none")

```

\clearpage

# Students enrolled in inscribe community and viewed a resource

Total number of students enrolled : 232

Number of students who viewed resources : 65

Percentage of students who viewed resources : 28.02%

\vspace{10mm}

```{r viewedResources2024, echo=FALSE}
# Example data
data <- data.frame(
  Category = c("Enrolled", "Viewed Resources", "Did Not Viewed Resource"),
  Count = c(232, 65, 232 - 65),
  Percentage = c(100, 28.02, 100 - 28.02)
)

# Create a bar plot
ggplot(data, aes(x = Category, y = Count, fill = Category)) +
  geom_bar(stat = "identity", color = "white") +
  labs(title = "Students' Interaction with Resources",
       y = "Number of Students") +
  geom_text(aes(label = paste0(Count, " (", sprintf("%.2f", Percentage), "%)")),
            position = position_stack(vjust = 0.5)) +
  theme_minimal() +
  theme(legend.position = "none")

```

\clearpage

## Spring A 2023 vs Spring A 2024

\vspace{5mm}

# Comparision of number of students enrolled in class sections compared to their enrollment in inscribe

\vspace{5mm}

Spring A 2023 : 

Total Students enrolled in respective class sections : 454

Number of Students enrolled in inscribe :  204

Spring A 2024 :

Total Students enrolled in respective class sections :  574

Number of Students enrolled in inscribe :  232

\vspace{10mm}

```{r EnrollmentCom, echo=FALSE}
# Example data
enrollment_data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Class_Sections = c(454, 574),
  Inscribe_Enrollment = c(204, 232)
)

# Reshape the data for ggplot2
enrollment_data_long <- tidyr::gather(enrollment_data, key = "Enrollment_Type", value = "Enrollment", -Semester)

# Create a grouped bar plot with data labels
ggplot(enrollment_data_long, aes(x = Semester, y = Enrollment, fill = Enrollment_Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Enrollment), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  labs(title = "Comparison of Enrollment for Spring A 2023 and Spring A 2024",
       x = "Semester",
       y = "Number of Students",
       fill = "Enrollment Type") +
  theme_minimal()
```

\clearpage

# Comparision of number of students who posted questions on inscribe 

Spring A 2023 : 

Number of students who posted questions in Inscribe community are 86. (It also includes students who just posted in Math Study Hall Channel)

Total students enrolled in inscribe : 204

Percentage of students : 42.16%

Spring A 2024 :

Number of students who posted questions in Inscribe community are 59. (It also includes students who just posted in Math Study Hall Channel)

Total students enrolled in inscribe : 232

Percentage of students : 17.77%

\vspace{10mm}

```{r QuestionsPosted, echo=FALSE}
# Example data
data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Posted_Questions = c(86, 59),
  Total_Enrolled = c(204, 232),
  Percentage = c(42.16, 17.77)
)

# Reshape the data for ggplot2
data_long <- tidyr::gather(data, key = "Variable", value = "Value", -Semester)

# Create a grouped bar plot
ggplot(data_long, aes(x = Semester, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Inscribe Community Engagement",
       x = "Semester",
       y = "Count/Percentage",
       fill = "Variable") +
  geom_text(aes(label = Value), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  theme_minimal()
```

\clearpage

# Comparision of number of students who viewed questions on inscribe 

Spring A 2023 : 

Number of students who viewed questions in Inscribe community are 170. (It also includes students who just viewed questions from Math Study Hall Channel)

Total students enrolled in inscribe : 204

Percentage of students : 83.33%

Spring A 2024 :

Number of students who viewed questions in Inscribe community are 151. (It also includes students who just viewed questions from Math Study Hall Channel)

Total students enrolled in inscribe : 232

Percentage of students : 68.97%

\vspace{10mm}

```{r QuestionsViewed, echo=FALSE}
# Example data
data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Viewed_Questions = c(170, 151),
  Total_Enrolled = c(204, 232),
  Percentage = c(83.33, 68.97)
)

# Reshape the data for ggplot2
data_long <- tidyr::gather(data, key = "Variable", value = "Value", -Semester)

# Create a grouped bar plot
ggplot(data_long, aes(x = Semester, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Inscribe Community Engagement",
       x = "Semester",
       y = "Count/Percentage",
       fill = "Variable") +
  geom_text(aes(label = Value), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  theme_minimal()
```

\clearpage

# Students who viewed questions/threads and also gave reactions

Spring A 2023 : 

Number of students who viewed questions and question threads : 170

Number of students who also gave reactions : 74

Percentage of students who gave reactions : 43.53%

Spring A 2024 : 

Number of students who viewed questions and question threads : 151

Number of students who also gave reactions : 45

Percentage of students who gave reactions : 29.80%

\vspace{10mm}

```{r GaveReactions, echo=FALSE}
# Example data
data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Gave_Reaction = c(74, 45),
  Viewed_Question = c(170, 151),
  Percentage = c(43.53, 29.80)
)

# Reshape the data for ggplot2
data_long <- tidyr::gather(data, key = "Variable", value = "Value", -Semester)

# Create a grouped bar plot
ggplot(data_long, aes(x = Semester, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Inscribe Community Engagement",
       x = "Semester",
       y = "Count/Percentage",
       fill = "Variable") +
  geom_text(aes(label = Value), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  theme_minimal()
```

\clearpage

# Students enrolled in inscribe community who posted resources 

Spring A 2023 : 

Total number of students enrolled : 204

Number of students who posted resources : 79

Percentage of students who posted resources : 38.73%

Spring A 2024 : 

Total number of students enrolled : 232

Number of students who posted resources : 49

Percentage of students who posted resources : 21.12%

\vspace{10mm}

```{r Postedresources, echo=FALSE}
# Example data
data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Posted_Resources = c(79,49),
  Enrolled = c(204,232),
  Percentage = c(38.73, 21.12)
)

# Reshape the data for ggplot2
data_long <- tidyr::gather(data, key = "Variable", value = "Value", -Semester)

# Create a grouped bar plot
ggplot(data_long, aes(x = Semester, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Inscribe Community Engagement",
       x = "Semester",
       y = "Count/Percentage",
       fill = "Variable") +
  geom_text(aes(label = Value), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  theme_minimal()
```

\clearpage

# Students enrolled in inscribe community who viewed Resources 

Spring A 2023 : 

Total number of students enrolled : 204

Number of students who viewed resources : 69

Percentage of students who viewed resources : 33.82%

Spring A 2024 : 

Total number of students enrolled : 232

Number of students who viewed resources : 65

Percentage of students who viewed resources : 28.02%

\vspace{10mm}

```{r ViewedResources, echo=FALSE}
# Example data
data <- data.frame(
  Semester = c("Spring A 2023", "Spring A 2024"),
  Viewed_Resources = c(69, 65),
  Enrolled = c(204, 232),
  Percentage = c(33.82, 28.02)
)

# Reshape the data for ggplot2
data_long <- tidyr::gather(data, key = "Variable", value = "Value", -Semester)

# Create a grouped bar plot
ggplot(data_long, aes(x = Semester, y = Value, fill = Variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Inscribe Community Engagement",
       x = "Semester",
       y = "Count/Percentage",
       fill = "Variable") +
  geom_text(aes(label = Value), position = position_dodge(width = 0.9), vjust = -0.5) +  # Add data labels
  theme_minimal()
```